% =============================================================
% Sapnanil — One‑Page ATS‑Friendly LaTeX Resume (Regenerated)
% Drop this .tex into Overleaf or your GitHub repo. No extra files needed.
% Packages are standard on TeX Live / Overleaf. pdflatex-compatible.
% -------------------------------------------------------------
% HOW TO EDIT:
% 1) Replace ALL CAPS placeholders (name, email, links, dates, etc.).
% 2) Keep bullets impact-focused; quantify with numbers where possible.
% 3) Avoid unescaped special chars: \%, \&, \_, #, $.
% =============================================================

\documentclass[11pt]{article}

% ---------- Packages ----------
\usepackage[margin=0.7in]{geometry}
\usepackage{parskip}            % no paragraph indents, nicer spacing
\usepackage{titlesec}           % compact section headers
\usepackage{enumitem}           % compact itemize
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage{ifthen}

% ---------- Section formatting ----------
\titlespacing*{\section}{0pt}{8pt}{4pt}
\titleformat{\section}{\large\bfseries}{}{0pt}{}
\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=2pt,parsep=0pt}

% ---------- Handy macros ----------
\newcommand{\sep}{\,\textbar\,}
\newcommand{\location}[1]{\hfill {\small #1}}
\newcommand{\daterange}[1]{\hfill {\small #1}}

% =============================================================
\begin{document}

% ---------- Header ----------
\begin{center}
  {\LARGE \textbf{SAPNANIL LASTNAME}}\\[4pt]
  \href{mailto:YOUREMAIL@example.com}{YOUREMAIL@example.com} \sep +91-XXXXXXXXXX \sep KOLKATA, INDIA \\[1pt]
  \href{https://www.linkedin.com/in/YOUR-LINK}{linkedin.com/in/YOUR-LINK} \sep
  \href{https://github.com/YOUR-USER}{github.com/YOUR-USER} \sep
  \href{https://tryhackme.com/p/YOUR-USER}{tryhackme.com/p/YOUR-USER} \sep
  \href{https://infernoradar.example}{infernoradar (blog)}
\end{center}

% ---------- Summary ----------
\section*{Summary}
Cybersecurity Engineer with 2+ years delivering Identity \& Access Management (SailPoint IIQ, IdentityNow) and security automation at scale. Builds least-privilege RBAC, scripts ops in PowerShell/Python, and partners with engineering to embed AppSec/Cloud Security (Azure) controls into SDLC. Focus: Application Security, Cloud Security, IAM, DevSecOps.

% ---------- Skills ----------
\section*{Skills}
\textbf{Domains:} Application Security, Cloud Security (Azure), IAM, Threat Modeling, Secure SDLC\\
\textbf{Tools:} Burp Suite, OWASP ZAP, Nmap, Wireshark, Git, Docker, GitHub Actions, Azure DevOps\\
\textbf{IAM:} SailPoint IIQ, IdentityNow; RBAC/ABAC; Access Reviews; Provisioning; JML flows\\
\textbf{Scripting:} PowerShell, Python, Bash \quad \textbf{Infra:} Linux, Networking, REST APIs\\
\textbf{Standards:} OWASP ASVS/Top 10, CIS Benchmarks, NIST CSF

% ---------- Experience ----------
\section*{Experience}
\textbf{EY (Ernst \& Young)} \emph{IAM Cybersecurity Consultant} \location{Remote (India)} \daterange{\textit{Oct 2022 -- Present}}\\
\begin{itemize}
  \item Implemented SailPoint IIQ/IdentityNow rules, connectors, and lifecycle events; automated joiner--mover--leaver, cutting manual provisioning time by ~50\%.
  \item Authored PowerShell/Python tooling for bulk access remediation and evidence export for access reviews; reduced weekly ops toil by 6--8 hours.
  \item Led role mining for least privilege; decomposed entitlements, mapped to business roles, and removed toxic combinations across high-risk apps.
  \item Embedded IAM controls into CI/CD and change processes; added runbooks and hardening guides for auditability and repeatability.
  \item Coordinated AppSec testing (Burp/ZAP); tracked findings and verified fixes pre-prod.
\end{itemize}

% ---------- Projects ----------
\section*{Selected Security Projects}
\textbf{AppSec CI Pipeline Hardening} \daterange{2025}\\
\begin{itemize}
  \item Integrated SAST (CodeQL/Bandit) and dependency scanning (OWASP Dependency-Check) into GitHub Actions with enforceable quality gates and issue automation.
\end{itemize}
\textbf{Least-Privilege Access Reviews at Scale} \daterange{2024}\\
\begin{itemize}
  \item Exported/normalized IIQ/IDN entitlements to CSV, mapped to business roles, and generated manager-friendly packs; ~30\% faster review cycles.
\end{itemize}
\textbf{Linux Hardening \& Audit} \daterange{2023}\\
\begin{itemize}
  \item Authored CIS-aligned baselines (SSH, sudoers, logging, patch cadence) via Ansible/PowerShell; improved audit findings and drift visibility.
\end{itemize}

% ---------- Certifications ----------
\section*{Certifications}
CompTIA Security+ (\emph{In progress, 2025}) \sep Microsoft AZ-500 (\emph{In progress, 2025}) \sep eJPT / ICCA (\emph{Planned})

% ---------- Education ----------
\section*{Education}
\textbf{Bachelor of Technology, Computer Science} \location{INDIA} \daterange{2018 -- 2022}\\
GPA: 7.2/10

% ---------- Achievements \& Community ----------
\section*{Achievements \& Community}
TryHackMe Premium (2025) \sep PowerShell automation projects on GitHub \sep Tech writing (InfernoRadar)

% -------------------------------------------------------------
% NOTES (commented) — delete or keep; not rendered in PDF
% - Keep resume to 1 page. Prioritize recent, quantified impact.
% - Mirror JD keywords (e.g., OWASP ASVS, Azure Key Vault, KMS, SailPoint connector dev).
% - Maintain variants in Git via branches or commented blocks.
% -------------------------------------------------------------

\end{document}
